Flesh Simulation in the Field of Animation

### 2020-04-07 LaTeX-Master-Vorlage/chapter/Background.tex
left to do: complete eigensystem

The behaviour of the object depends heavily on the material it consists of. This will be further explained in the next section concerning \textit{Material Constants}. In order to get a convincing simulation for a specific material, we have to choose an appropriate energy function. The behaviour of human flesh can be put into the category of hyperelastic materials. The key property of elasticity is, that if all the forces that are applied over an object are removed, the object recovers into its original shape and volume (\cite{KORSUNSKY20175}, p. 5).

>>>>

The behaviour of the object depends heavily on the material it consists of. This will be further explained in the next section concerning \textit{Material Constants}. In order to get a convincing simulation for a specific material, we have to choose an appropriate energy function. The behaviour of human flesh can be put into the category of hyperelastic materials. The key property of elasticity is, that if all the forces that are applied over an object are removed, the object recovers into its original shape and volume (\cite{KORSUNSKY20175}, p. 5). For deformations of elastic materials, the Hooke's equation holds to some extend. Hooke's law describes a linear relationship of the applied force and the distance to the original position of a spring:
\[
	F = kx
\]
\textit{F} decribes the force, \textit{x} the distance and \textit{k} is a constant value. Material for which this equation holds are called linear-elastic or Hookean.

\todoredefined[inline]{
TODO: Explain Hooke better and add source for hookean, Neo-Hookean Model in Hyperelasticity
}

### 2020-04-07 LaTeX-Master-Vorlage/chapter/paper.tex
left to do: complete eigensystem

\todoredefined[inline]{
TODO: explain how to get to equation with singular values
}

@@

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term can be written as $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

\todoredefined[inline]{
TODO: How much needs to be explained here?
}

\subsection{Lamé Reparametrization}
\todoredefined[inline]{
TODO: How much needs to be explained here?
}

@@

\subsubsection{Extreme values}
We can test the energy with some extreme values. For a very low poisson's value, I choose $\lambda = 0.1$ and $\mu = 10.0$ with a resolution of $30$. This takes about $100$ to $200$ Newton iterations. I increased the original limit of a maximum of $50$ Newton iterations per step because the solve failed to get the result within these $50$ iterations. The finished result gives us some strange looking deformations as shown in Fig. -. But since the goal is to simulate human flesh, we are not very concerned how the energy performs with a low poissson's ratio.

\begin{figure}[!ht]
\centering
\includegraphics[width=.7\textwidth]{resources/mu_extreme_small.png}  
\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
\label{fig:mu_extreme}
\end{figure}

>>>>

\todoredefined[inline]{
TODO: explain how to get to equation with singular values?
}

@@

\subsection{Meta-Stability under Degeneracy}
We have seen that he energy $\Psi_{E}$ has inversion, reflection and rest stability. Now we are interested how it behaves under degeneracy. The authors of the paper \textit{\acrshort{snh}} viewed this as a Drucker stability analysis (see \cite{bower2009applied}). By Drucker stability, we mean a set of criteria that a material can satisfy or not. This is a measurement of the stability of the material. The calculations can be found in the supplemental material of \textit{\acrshort{snh}}, I will only present the results here.

The energy remains stable when crushing the object into a \textit{plane}. The object is able to return to its rest state. Thus, no further adjustments needs to be done. When crushing the object into a \textit{line}, the energy is meta-stable. A meta-stable state is a weaker state of stability that is resistant to small changes but not to large ones. The alternative would be a state that yields singularities, which worsens the situation. Hence, we can leave the energy as it is. Crushing the object to a \textit{point}, the material cannot recover into its rest state. This effect is small for a higher poisson's ratio as for biological tissue. For completeness the authors nevertheless added a regularized origin barrier:
\[
	\Psi_{origin} = \operatorname{log}(I_C +\delta)
\]
This term eliminates the point meta-stability for a positive poisson's ratio without interfering with the other requirements for the energy. It can be shown that the value $\delta$ should be set to $1$. This is also included in the supplemental material of the paper (\cite{Smith:2018:SNF:3191713.3180491}, 12:4).

The final energy is then
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term can be written as $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

\subsection{Lamé Reparametrization}
In order to stay consistent with Hooke's law, we need to do a reparametrization of $\mu$ and $\lambda$. For achieving this, we set
\begin{equation}
	\mathbf{P}(\mathbf{F}) = 2 \mu_{Lamé} \epsilon + \lambda_{Lamé} \operatorname{tr}(\epsilon) \mathbf{I},
\end{equation}
where $\epsilon = \frac{1}{2} (\mathbf{F} + \mathbf{F}^\intercal) - \mathbf{I}$ is the linearized strain tensor. We then set $\mu = \frac{4}{3} \mu_{Lamé}$ and $\lambda = \lambda_{Lamé} + \frac{5}{6} \mu_{Lamé}$. The equation for the poisson's ratio then shifts to 
\[
	v= \frac{\lambda - \left( \frac{5}{8} \right) \mu}{2 \left(\lambda + \left( \frac{1}{8} \mu \right) \right)}.
\]

\todoredefined[inline]{
TODO: Do a better job here.
}

@@

\subsubsection{Extreme values}
We can test the energy with some extreme values. For getting a very low poisson's value near 0, I choose $\lambda = 0.1$ and $\mu = 10.0$ with a resolution of $30$. This takes about $100$ to $200$ Newton iterations. The finished result gives us a strange looking deformations and little artefacts as shown in Fig. \ref{fig:mu_extreme}. This does not mean that it is a bad model, but rather that is only suited for higher poisson's ratio like it is the case for simulating flesh.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/mu_extreme_1.png}
	\caption{Step 4 with $\lambda = 0.1$ and $\mu = 10.0$ on a tetrahedral mesh shown from above}
	\label{fig:mu_extreme}
\end{figure}
